---
title: "MAsim-tutorial"
author: "Katharine Banner"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r funs, echo = FALSE, message=FALSE}
devtools::load_all("../../MApp-Rpackage/MApp/.")
devtools::load_all("../../MAsim/.")
```

This vignette contains the R code used for simulating and displaying the results discussed in Chapter 3 of Katharine Banner's dissertation. 

# Simulation Code

The code provided in Katharine Banner's Github repositories `MAsim` ([https://github.com/kbanner14/MAsim](https://github.com/kbanner14/MAsim)) and `MApp-Rpackage/MApp` ([https://github.com/kbanner14/MApp-Rpackage/MApp](https://github.com/kbanner14/MApp-Rpackage/MApp)) contain all functions to recreate the results presented in Chapter 3. Both packages can be installed using `devtools::install_github()` or by downloading the repository and loading the packages using `devtools::load\_all("PATH/TO/MAsim/.")`. Once the packages are loaded, the user can generate the simulated results using the code in Section \ref{sec:recreate}. 

```{r load, echo = TRUE, cache = TRUE, eval = FALSE}
# install MApp through github
devtools::install_github("kbanner14/MApp-Rpackage", subdir = "MApp")
# or load MApp from local directory
devtools::load_all("PATH/TO/MApp-Rpackage-master/MApp/.")

# install MAsim through github
devtools::install_github("kbanner14/MAsim")
# or load MAsim from local directory
devtools::load_all("PATH/TO/MAsim/.")
```


# Recreate the Simulation
\label{sec:recreate}

The following code generates the same results presented in Chapter 3. 

```{r dataGen, echo = TRUE, cache=TRUE}
# reference case
#~~~~~~~~~~~~~~~~~~~~#
#  300 realizations  #
#~~~~~~~~~~~~~~~~~~~~#

set.seed(1)
cor_0 <- sim_d2(300, cor_x = 0.0, tol = 0.01)

set.seed(6)
cor_3 <- sim_d2(300, cor_x = 0.3, tol = 0.01)

set.seed(5)
cor_6 <- sim_d2(300, cor_x = 0.6, tol = 0.01)

set.seed(4)
cor_7 <- sim_d2(300, cor_x = 0.7, tol = 0.01)

set.seed(3)
cor_8 <- sim_d2(300, cor_x = 0.8, tol = 0.01)

set.seed(8)
cor_9 <- sim_d2(300, cor_x = 0.9, tol = 0.01)

df_vec <- c(cor_0, cor_3, cor_6, cor_7, cor_8, cor_9)

# comparing signal to noise Truth = YES

set.seed(1)
cor_0s1 <- sim_d2(300, cor_x = 0.0, tol = 0.01, sig_y = 1)

set.seed(6)
cor_3s1 <- sim_d2(300, cor_x = 0.3, tol = 0.01, sig_y = 1)

set.seed(5)
cor_6s1 <- sim_d2(300, cor_x = 0.6, tol = 0.01, sig_y = 1)

set.seed(4)
cor_7s1 <- sim_d2(300, cor_x = 0.7, tol = 0.01, sig_y = 1)

set.seed(3)
cor_8s1 <- sim_d2(300, cor_x = 0.8, tol = 0.01, sig_y = 1)

set.seed(8)
cor_9s1 <- sim_d2(300, cor_x = 0.9, tol = 0.01, sig_y = 1)

df_vec_s1 <- c(cor_0s1, cor_3s1, cor_6s1, cor_7s1, cor_8s1, cor_9s1)


# comparing truth in the model set sig-y = low

# NO5
set.seed(1)
cor_0n5 <- sim_d2(300, cor_x = 0.0, tol = 0.01, case = 2)

set.seed(6)
cor_3n5 <- sim_d2(300, cor_x = 0.3, tol = 0.01, case = 2)

set.seed(5)
cor_6n5 <- sim_d2(300, cor_x = 0.6, tol = 0.01, case = 2)

set.seed(4)
cor_7n5 <- sim_d2(300, cor_x = 0.7, tol = 0.01, case = 2)

set.seed(3)
cor_8n5 <- sim_d2(300, cor_x = 0.8, tol = 0.01, case = 2)


set.seed(8)
cor_9n5 <- sim_d2(300, cor_x = 0.9, tol = 0.01, case = 2)

df_vec_n5 <- c(cor_0n5, cor_3n5, cor_6n5, cor_7n5, cor_8n5, cor_9n5)

# NO 4 
set.seed(1)
cor_0n4 <- sim_d2(300, cor_x = 0.0, tol = 0.01, truth4 = T)

set.seed(6)
cor_3n4 <- sim_d2(300, cor_x = 0.3, tol = 0.01, truth4 = T)

set.seed(5)
cor_6n4 <- sim_d2(300, cor_x = 0.6, tol = 0.01, truth4 = T)

set.seed(4)
cor_7n4 <- sim_d2(300, cor_x = 0.7, tol = 0.01, truth4 = T)

set.seed(3)
cor_8n4 <- sim_d2(300, cor_x = 0.8, tol = 0.01, truth4 = T)

set.seed(8)
cor_9n4 <- sim_d2(300, cor_x = 0.9, tol = 0.01, truth4 = T)

df_vec_n4 <- c(cor_0n4, cor_3n4, cor_6n4, cor_7n4, cor_8n4, cor_9n4)

# comparing truth in the model set for sig to noise = High

## truth = NO4, sig = 1

set.seed(1)
cor_0n41 <- sim_d2(300, cor_x = 0.0, tol = 0.01, truth4 = T, sig_y = 1)

set.seed(6)
cor_3n41 <- sim_d2(300, cor_x = 0.3, tol = 0.01, truth4 = T, sig_y = 1)

set.seed(5)
cor_6n41 <- sim_d2(300, cor_x = 0.6, tol = 0.01, truth4 = T, sig_y = 1)

set.seed(4)
cor_7n41 <- sim_d2(300, cor_x = 0.7, tol = 0.01, truth4 = T, sig_y = 1)

set.seed(3)
cor_8n41 <- sim_d2(300, cor_x = 0.8, tol = 0.01, truth4 = T, sig_y = 1)

set.seed(8)
cor_9n41 <- sim_d2(300, cor_x = 0.9, tol = 0.01, truth4 = T, sig_y = 1)

df_vec_n41 <- c(cor_0n41, cor_3n41, cor_6n41, cor_7n41, cor_8n41, cor_9n41)

# truth = NO5, sig = 1 

set.seed(1)
cor_0n51 <- sim_d2(300, cor_x = 0.0, tol = 0.01, case = 2, sig_y = 1)

set.seed(6)
cor_3n51 <- sim_d2(300, cor_x = 0.3, tol = 0.01, case = 2, sig_y = 1)

set.seed(5)
cor_6n51 <- sim_d2(300, cor_x = 0.6, tol = 0.01, case = 2, sig_y = 1)

set.seed(4)
cor_7n51 <- sim_d2(300, cor_x = 0.7, tol = 0.01, case = 2, sig_y = 1)

set.seed(3)
cor_8n51 <- sim_d2(300, cor_x = 0.8, tol = 0.01, case = 2, sig_y = 1)

set.seed(8)
cor_9n51 <- sim_d2(300, cor_x = 0.9, tol = 0.01, case = 2, sig_y = 1)

df_vec_n51 <- c(cor_0n51, cor_3n51, cor_6n51, cor_7n51, cor_8n51, cor_9n51)
```

#Recreating Simulation Study Results

We discussed results from select treatments in Chapter \ref{CH:3}. Here, we provide instructions for creating plots to summarize results from other treatments. For all of the plotting functions discussed below, the `y = "d"` tells the function to use $Var_{MA}/VAR_{Cts}$ as the response variable. The argument `y` can take on the following characters: $Var_{Cts}/Var_{top}$ = `"d_topCts"`, $Var_{MA}/Var_{top}$ = `"d_topMA"`, $SD_{MA} - SD_{top}$ = `diff_MAt`, and $SD_{Cts} - SD_{top}$ = `diff_ct`. 

## Using `pres_d_plot` to Visualize Results

Use `pres_d_plot` to plot results from all levels of correlation for fixed levels of truth in the model set and signal to noise. Specify the number of variables with `n_var` and the upper limit for the $y$-axis with `y_max`.

```{r cor-ref, echo = TRUE, out.width='.7\\linewidth', fig.width = 10, fig.height = 8, cache= TRUE, fig.cap = "Low signal to noise, truth = YES, all correlations", fig.align = "center"}
pres_d_plot(df_vec, y = "d", n_var = 5, y_max = 3.5)
```

Use `plot_order = "backward"` to plot results from $X_5$ first and $X_1$ last.

```{r cor-ref2, echo = TRUE, out.width='.7\\linewidth', fig.width = 10, fig.height = 8, cache= TRUE, fig.cap = "Low signal to noise, truth = YES, all correlations, plotted X5:X1", fig.align = "center"}
pres_d_plot(df_vec, y = "d", n_var = 5, plot_order = "backward", y_max = 3.5)
```

To create plots from different treatments use a different list of results (e.g., to plot results from high signal to noise and truth in the model set, use `df_vec_s1` in place of `df_vec`). 

## Using `pres_y` to Visualize Results

If you prefer looking at one individual treatment combination for all variables considered (in their own plots), use `pres_y`. You must specify the correlation with `cor_x` and you may specify a maximum value for the $y$-axis with `y_max`. Note, rather than using the list of results for all correlations and fixed levels of signal to noise and truth in the model set, use the individual results from one treatment. 

```{r ind-ref, echo = TRUE, out.width='.7\\linewidth', fig.width = 10, fig.height = 8, cache= TRUE,fig.cap = "Low signal to noise, truth = YES, cor = 0.9", fig.align = "center" }
pres_y(cor_9, y = "d", cor_x = 0.9, y_max = 3.5)
```

## Using `pres_trt_compare` to Visualize Results

Use `pres_trt_compare` to compare results from two specific treatments. Here, I use this function to compare low signal to noise to high signal to noise for truth in the model set and correlation equal to 0.9. Specify the upper limit for the $y$-axis with `y_max`, the response variable with `y`, the correlation between $X_3$ and $X_5$ with `cor_x`, and labels for the treatments being compared with `labs`.


```{r sig1-ref9, echo = TRUE, out.width='.7\\linewidth', fig.width = 10, fig.height = 8,fig.align = "center", fig.cap = "Comparing signal to noise: Low vs. High signal to noise, truth = YES, all correlations", cache= FALSE}
pres_trt_comp(c(cor_9, cor_9s1), y = "d", cor_x = 0.9, 
				labs = c("sig-y = 2.5, YES", "sig-y = 1, YES"), y_max = 3.5)
```


## Using `pres_y_compare` to Visualize Results

Use `pres_y_compare` to compare results from two response variables for a particular treatment. Here, I use this function to compare $Var_{MA}/Var_{cts}$ to $Var_{MA}/Var_{top}$ for low signal to noise, truth in the model set, and correlation equal to 0.9. Specify the upper limit for the $y$-axis with `y_max`, the response variable with `y`, the correlation between $X_3$ and $X_5$ with `cor_x`, and labels for the ratios of variances being compared with `labs`.

```{r sig2-yes9, echo = TRUE, out.width='.7\\linewidth', fig.width = 10, fig.height = 8,fig.align = "center", cache= TRUE, fig.cap = "Comparing two ratios of varainces: Low signal to noise, truth = YES, all correlations"}
pres_y_comp(cor_9, y_vec = c("d", "d_topMA"), 
			 labs = c("Var_MA/Var_cts", "Var_MA/Var_top"), cor_x = 0.9, y_max = 8)
```


## Using `final_bean_d` to Visualize Results 

Use `final_bean_d` to visualize results for $Var_{cts}/Var_{top}$ across all correlations for fixed levels of signal to noise and truth in the model set.  

```{r bean-all, echo = TRUE, out.width='.7\\linewidth', fig.width = 10, fig.height = 8,fig.align = "center", cache= TRUE, fig.cap="Low signal to noise, truth = YES, cor = 0.9"}
final_bean_d(df_vec, y = "d_topCts")
```


## Using `final_bean_diff` to Visualize Results 

Use `final_bean_diff` to visualize results for $SD_{MA} - SD_{cts}$ across all correlations for fixed levels of signal to noise and truth in the model set.  

```{r bean-diff, echo = TRUE, out.width='.7\\linewidth', fig.width = 10, fig.height = 8,fig.align = "center", cache= TRUE, fig.cap="Low signal to noise, truth = YES, cor = 0.9"}
final_bean_d(df_vec, y = "d_topCts")
```

